---
title: "HW10"
author: "Dominika Markowska-Desvallons"
date: "10/30/2020"
output: html_document
---
### Assigment 10 

In this assignment, you should start by getting the primary example code from chapter 2 working in an R Markdown document.  You should provide a citation to this base code.  You’re then asked to extend the code in two ways:

- Work with a different corpus of your choosing, and

- Incorporate at least one additional sentiment lexicon (possibly from another R package that you’ve found through research).



## Setting up the example code from ‘Text Mining with R’ Chapter 2.

  “2 Sentiment Analysis with Tidy Data.” Text Mining with R: a Tidy Approach, by Julia Silge and David Robinson, O’Reilly Media, 2017.
  https://www.tidytextmining.com/sentiment.html
```{r}
library(tidyverse)
library(tidytext)
library(dplyr)
get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")
```



```{r}

library(janeaustenr)
library(dplyr)


library(stringr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
      ignore_case = TRUE
    )))
  ) %>%
  ungroup() %>%
  unnest_tokens(word, text)

nrc_joy <- get_sentiments("nrc") %>%
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
  
```
## Setting up New Corpus - .

we will use the function gutenberg_metadata from the package gutenbergr to check the id of the books we are interested in analyzing.


```{r}
library(gutenbergr)
gutenberg_metadata %>%
  filter(title == "Crime and Punishment")


```

 “Crime and Punishment” is 2554 for the English version.


```{r}
crime_punishment <- gutenberg_download(2554)
glimpse(crime_punishment)


```

# Tydying book

```{r}

tydying_crime_punishment <- crime_punishment %>%
  slice(-c(1:102)) %>%
  mutate(line_num = row_number(),
         part = cumsum(str_detect(text, regex("^PART [\\divxlc]",
                                                  ignore_case = TRUE)))) %>%  
         group_by(part) %>%
         mutate(chapter = cumsum(str_detect(text, regex("^CHAPTER [\\divxlc]",
                                                          ignore_case = TRUE)))) %>% 
         ungroup()

glimpse(tydying_crime_punishment)
```
creating a new column where each row has only one word


```{r}

Book <- tydying_crime_punishment %>% 
  unnest_tokens(word, text) %>%
  mutate(word = str_replace(word, "_", ""))


#now removing stop words said
Text_CP <- Book %>%
  anti_join(stop_words, by = "word")
```

### Analyzing Word Frequency

```{r}
Text_CP%>%
  count(word, sort = TRUE) %>%
  top_n(10, n) %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, fill = word)) +
  geom_col(show.legend = FALSE) +
  scale_fill_viridis_d(option = "viridis") +
  coord_flip() +
  xlab(NULL) +
  labs(title = "Crime and Punishment- Word Frequency") +
  theme_minimal()
```

The most used word more is  the name of the main character, Raskolnikov.


### Sentiment Analysis using nrc
```{r}
Text_CP %>%
  inner_join(get_sentiments("nrc")) %>%
  count(index = line_num %/% 150, sentiment) %>% 
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  ggplot(aes(x = index, sentiment)) +
  geom_col(fill = "red", show.legend = FALSE) +
  labs(title = "Sentiment Analysis ") +
  theme_minimal()
```


we can see that book has  more negative sentiment than positive one

```{r}
Text_CP %>%
  inner_join(get_sentiments("nrc")) %>%
  count(sentiment) %>%
  mutate(total = sum(n),
         prop = n / total) %>%
  ggplot(aes(fct_reorder(sentiment, prop), y = prop, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  scale_fill_viridis_d(option = "viridis") +
  xlab(NULL) +
  ggtitle("Sentiment Analysis ") +
  coord_flip() +
  theme_minimal()
```


In conclusion, nrc package provides wider variety of words like negative and positive but as well other feeling assosiate with like joy and anger and so on. 

