---
title: "HW_3"
author: "Dominika Markowska-Desvallons"
date: "9/12/2020"
output: html_document
---
#1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS" 
```{r}
url  <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
majors <- read.csv(paste0(url), header = TRUE)
#head(majors)

df <- data.frame(majors)
majors_list <- subset(df, grepl("DATA", Major) | grepl("STATISTICS", Major))

majors_list
```
#2 Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
```{r}
library(stringr)

fruits<- c("bell pepper","bilberry", "blackberry" ,"blood orange",
"blueberry", "cantaloupe","chili pepper","cloudberry",  
"elderberry","lime", "lychee", "mulberry","olive" ,"salal berry")


fruits_l <- writeLines(str_c(dQuote(fruits),collapse =","))

```

#3 Describe, in words, what these expressions will match:

(.)\1\1 --it matches the same character appearing three times in a row. 
"(.)(.)\\2\\1" --it matches a pair of characters followed by the same pair of characters in reversed order. 
(..)\1 - - Looks for any two characters repeated. 
"(.).\\1.\\1" -- Looks for a character followed by any character, the original character, any other character, the original character again.ex. 'abata'
"(.)(.)(.).*\\3\\2\\1"` --- Looks for three characters followed by zero or more characters of any kind followed by the same three characters but in reverse order.

#4 Construct regular expressions to match words that:

Start and end with the same character.
```{r}
str_view(c("lol","kayak","doll"),"(.).*\\1")
```
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}

str_view(c("church","choclate","chacha"),"(..).*\\1")
```
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r}

str_view(c("eleven","banana","apple","aparat"),"(.).*\\1.*\\1")
```

